ICBEdataset_paper_figure_prep

### 2022-03-22 README.Rmd
tsv to readme
plot reorder

The agreed datasets are the final dataset used in much of the paper and figures. It includes our best efforts at cleaning the data and reconciling intercoder agreement. The dataset is available in long and wide format.

@@

  - CaseStudy196
      + creates Cuban Missile Crisis comparison table `/tables/CaseStudy196_ft.Rds`. 
  - CaseStudy426
      + creates DRC Civil War comparison table `/tables/CaseStudy426_ft.Rds`. 
  - ICBEdataset_figure_metro_maps
      + creates the metroplot Rds files in `/figures/metro_plots/.`.
  - ICBEdataset_figure_semantic_embeddings
      + creates the figure `/figures/p_semantic_embeddings.png` and the `/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds` and `/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds`
  - ICBEdataset_paper_appendixICBCrises
      +  creates `/tables/ft_crisis_text_counts.Rds`.
  - ICBEdataset_paper_appendixVerbMeanings
      + creates `/tables/verbs_sentence_wordnet_top_ft.Rds`
  - ICBEdataset_paper_figure_prep
      + creates the metroplot pngs in `/figures/.`.
  - ICBEdataset_paper_litreviewtable
      + creates the table `/tables/litreview_ft.Rds`. 
  - ICBEdataset_paper_PlotInterCoderAgreement
      + creates the figure `figures/p_percent_chose_tag_by_concept.png`

>>>>

The agreed datasets are the final dataset used in much of the paper and figures. It includes our best efforts at cleaning the data and reconciling intercoder agreement. The dataset is available in long and wide format. The data is also available in .tsv format in the same folders.

@@

  - 04_ICBEdataset_paper_litreviewtable
      + creates the table `/tables/litreview_ft.Rds`.
  - 05_ICBEdataset_paper_PlotInterCoderAgreement
      + creates the figure `figures/p_percent_chose_tag_by_concept.png`
  - 06_ICBEdataset_figure_metro_maps
      + creates the metroplot Rds files in `/figures/metro_plots/.`.
  - 07_ICBEdataset_figure_semantic_embeddings
      + creates the figure `/figures/p_semantic_embeddings.png` and the `/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds` and `/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds`
  - 08_CaseStudy196
      + creates Cuban Missile Crisis comparison table `/tables/CaseStudy196_ft.Rds`. 
  - 09_CaseStudy426
      + creates DRC Civil War comparison table `/tables/CaseStudy426_ft.Rds`. 
  - 10_ICBEdataset_paper_figure_prep
      + creates the metroplot pngs in `/figures/.`.
  - 11_ICBEdataset_paper_appendixICBCrises
      +  creates `/tables/ft_crisis_text_counts.Rds`.
  - 12_ICBEdataset_paper_appendixVerbMeanings
      + creates `/tables/verbs_sentence_wordnet_top_ft.Rds`

### 2022-03-22 replication_paper/rmd/10_ICBEdataset_paper_figure_prep.Rmd
plot reorder

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
#ICBe  196
library(ggplot2)
p_metro_plot <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
actor_colors <- p_metro_plot$actor_colors

>>>>

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
#ICBe  196
library(ggplot2)
p_metro_plot <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))

actor_colors <- p_metro_plot$actor_colors
